Home Nighttime Cough Monitoring

### 2025-03-05 Lilah Melzer/cough_monitor_analysis.qmd
cough monitor plots finished

```{r}
#| label: fig-coughs-dist
#| fig-cap: Histogram of Coughs Across All Nights
#| warning: false
ggplot(agg_counts, aes(x = Coughs)) +
  geom_histogram(binwidth = 1)
```

@@

@@

>>>>

```{r}
#| label: fig-coughs-dist
#| fig-cap: Histogram of Coughs Across All Nights
#| warning: false
hist <- ggplot(agg_counts, aes(x = Coughs)) +
  geom_histogram() +
  theme_bw() +
  theme(axis.title.y = element_blank())
hist
ggsave("/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Dissemination/Figures/histogram.png",
  plot = hist, width = 9, height = 6, units = "in"
)
```

@@

## Association with coughs

There were no statistically significant correlations between coughs and survey respiratory scores.

@@

## Association with coughs

There were no statistically significant correlations between coughs and survey scores.

# Participant figures

```{r}
#| warning: false
cfqr_children_6_11$sid <- as.numeric(cfqr_children_6_11$sid)
cfqr_parent_6_13$sid <- as.numeric(cfqr_parent_6_13$sid)
p38 <- full_join(
  agg_counts,
  cfqr_children_6_11 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Children Ages 6-11` = respirat),
  by = join_by(sid, Date)
)
p38 <- full_join(
  p38,
  cfqr_parent_6_13 %>% select(sid, Date, respirat) %>%
    rename(`CFQ-R Caregivers 6-13` = respirat),
  by = join_by(sid, Date)
)
p38 <- p38 %>%
  filter(sid == 38) %>%
  pivot_longer(c(Coughs, `CFQ-R Children Ages 6-11`, `CFQ-R Caregivers 6-13`)) %>%
  filter(!is.na(value))
p38$name <- factor(p38$name,
  levels = c("Coughs", "CFQ-R Children Ages 6-11", "CFQ-R Caregivers 6-13")
)
p38_plot <- ggplot(p38, aes(x = Night, y = value)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  facet_wrap(~name, nrow = 3, scales = "free")
p38_plot
ggsave("/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Dissemination/Figures/participant_38.png",
  plot = p38_plot, width = 9, height = 7, units = "in"
)
```
